---
title: "Lab 1"
author: "Yealim Sung"
date: "Assigned: 09/03/2019"
output: 
  html_document:
      number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Collaborating on a Repository

**Step 1** 

    - Name?: Yealim Sung
    - What do you tell people about your field of study at a party?: Computer stuff
    - What are the three most important tools/strategies you use for organizing your work?: sticky notes, pencil case, and notepad
    - Interesting fact about yourself?: I lived in three different countries.

# Understanding Concepts 

You may work on this with your partner or individually. 

  1. Explain the difference between Git and Github.
  
  2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 

  3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 

# Coding Exercises 

  You may work on this with your partner or individually. 

  1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.

  2. Run the following code: 

   ```{r}
   age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   ```
   
  This code took three vectors (`age`, `smoker`, and `weight`) and binded them together into an `R` object known as a 
  `data.frame`. The advantage of `data.frame` is that it can handle vectors of different types. For example, age is a numeric 
    vector but smoker status is a character vector (T or F). We named this `data.frame` as `example_data`. I obviously made a
    data entry error: someone cannot have 0 weight. The correct weight should be 150 pounds. Write one line of code that can
    easily correct this using the `[]` syntax. 


  3. In the following I have two code snippets. Turn these code snippets into functions. Think about what each function does
  and what you would name it. How many arguments does it need? 
  ```{r, eval=FALSE}
  mean(is.na(x))

  x / sum(x, na.rm = TRUE)
  ```
  
4. Write a function named `both_na()`. This function take two vectors of the same length and returns the number of positions that have an `NA` value in both vectors. 

# Submission 

Once you have finished Lab 1 and after committing all of your work (don't forget to first 'git add FILENAMES'), you should  push your work to GitHub. 

Then each student (not team) should send an email titled  
`ds202 lab1` (case-sensitive) to the grader, Yunhui Qi <qyh@iastate.edu>, before by 10 pm on Thursday Sept 5. The email should contain *only* 

- Your name, student ID, github username, and GitHub repo name for Lab1, and 
- Your partner's github username, and your partner's repo name to which you made changes. 

**Note:**
Make sure that each team member has collaborated on the other member's repo. Your homework score will be the sum of each team member's score. Help out your team member in case he/she is stuck. 